Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2019-09-02 code/98-paper/ieee/ieee-manuscript.tex
save state

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Supporting Ecological Decision Making Using Feature-Selection and Variable Importance}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% learner
% - RF Car is the overall winner
% - Ridge-CV hit and miss (hit = NRI, miss = VI)
% - all MBO penalized methods have no difference across tasks
Random Forest combined with the "Carscore" filter showed the best absolute performance (RMSE of 3.396).
A noticable difference between SVM and all other learners was visible for all feature sets without NRI variables (difference in RMSE of 3-4).
L1 penalized regression showed slightly better results in three out of six tasks when being optimized using the package internal 10-fold CV compared to MBO (RMSE of 50 vs 58).
Regression with Ridge penalty showed a high variance when comparing results across tasks: In three out of six tasks (all including VI variables) the error was out of bounds (HR-NRI-VI; HR-VI, VI), for HR-NRI and HR the error was medium (around 40 RMSE), and for task NRI Ridge regression achieved almost the same score as the best performing model (3.39 RMSE, NRI).
All penalized methods tuned using MBO showed exactly the same error across all tasks.

@@

% FIXME: add table of first 20(?) ordered performance results across all tasks

>>>>

\usepackage{booktabs}
\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Supporting Ecological Decision Making Using Feature-Selection and Variable Importance}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% learner
% - RF Car is the overall winner
% - Ridge-CV hit and miss (hit = NRI, miss = VI)
% - all MBO penalized methods have no difference across tasks
Random Forest combined with the "Carscore" filter showed the best absolute performance (RMSE of 3.396) (\autoref{tab:perf-top-15}).
A noticable difference between SVM and all other learners was visible for all feature sets without NRI variables (difference in RMSE of 3-4).
Considering a grouped performance by learners across all tasks and filters, SVM showed the most robust results (\autoref{tab:perf-top-15}).
L1 penalized regression showed slightly better results in three out of six tasks when being optimized using the package internal 10-fold CV compared to MBO (RMSE of 50 vs 58).
Regression with Ridge penalty (L2) showed a high variance when comparing results across tasks: In three out of six tasks (all including VI variables) the error was out of bounds (HR-NRI-VI; HR-VI, VI), for HR-NRI and HR the error was medium (around 40 RMSE), and for task NRI Ridge regression achieved almost the same score as the best performing model (3.39 RMSE, NRI) (\autoref{tab:perf-top-15}).
All penalized methods tuned using MBO showed exactly the same error across all tasks.

@@

\input{performance-top-20}

\input{performance-best-per-learner.tex}
